### 2012-04-08 docs/architecture/architecture.tex
remove setbc

The actual filling of the ghostcells according to the descriptions
contained in the \bctower\ is carried out by the {\tt setbc} routine,
which is called by {\tt multifab\_physbc}.

>>>>

The actual filling of the ghostcells according to the descriptions
contained in the \bctower\ is carried out by the {\tt multifab\_physbc}
routine.
